---
title: "Simple document"
author: "jeff Goldsmith"
date: "2023-09-12"
output: github_document
---


```{r}
library(tidyverse)
```

I'm an R Markdown document! 

# Section 1: First code chunk

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2: Make a plot
ˆ
```{r}
plot_df = 
  tibble(
    x = rnorm(1000, sd = 0.5),
    y = 1 + 2 * x + rnorm(1000),
  )
```

Next up is a histogram of the "x" variable in "plot_df"

```{r}
ggplot(plot_df, aes (x=x))+geom_histogram()
```

# Section 3: 

```{r}
ggplot(plot_df, aes (x=x, y=y))+geom_point()
```


# Section 4: 

This code chunk should creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element.

```{r la_df}
la_df =
  tibble(
    num_samp = rnorm(500, mean = 1),
    log_vec = num_samp > 0,
    abs_val = abs(num_samp)
  )
ggplot(la_df, aes(x = abs_val)) + geom_histogram()
```



This code is borrowed form last lecture; it creats a dataframe for plotting.

I can take the mean of the sample, too!
The mean is `r mean(samp)`.